Actuator line modeling of vertical-axis turbines

### 2016-08-27 paper.tex
Fix broken crossref
Fix typo

Both the high solidity UNH-RVAT and medium solidity RM2 turbines were modeled
using the ALM inside a Reynolds-averaged Navier--Stokes (RANS) simulation,
closed with the standard $k$--$\epsilon$ turbulence model. These rotors provide
diverse parameters, which helped evaluate the robustness of the ALM. The
simulations were performed inside a domain similar in size to that used in
\cite{Bachant2016-BR-CFD} to approximately (including blockage) the tow tank
experiments (3.66 m wide, 2.44 m tall, 1.52 m upstream and 2.16 m downstream),
with similar velocity boundary conditions: 1 m/s inflow, no-slip (fixed to 1
m/s) walls and bottom, and a rigid slip condition for the top, to approximate
some effects of the tow tank's free surface. Simulations were run for a total of
6 seconds, with the latter half used to calculate performance and wake
statistics. Pressure--velocity coupling for the momentum equation was achieved
using the PISO (pressure implicit splitting of operators) method. A slice of the
mesh in the $x$--$y$ plane is shown in Figure~\ref{fig:ALM-mesh}.

@@

The near-wake's mean velocity field at $x/D=1$ is shown in
Figure~\ref{RVAT-ALM-LES-meancontquiv}. Compared with the RANS ALM results, the
LES looks much more like the blade-resolved and experimental results
\cite{Bachant2015-JoT}, showing the clockwise and counterclockwise mean swirling
motion on the $-y$ and $+y$ sides of the rotor, respectively.

>>>>

Both the high solidity UNH-RVAT and medium solidity RM2 turbines were modeled
using the ALM inside a Reynolds-averaged Navier--Stokes (RANS) simulation,
closed with the standard $k$--$\epsilon$ turbulence model. These rotors provide
diverse parameters, which helped evaluate the robustness of the ALM. The
simulations were performed inside a domain similar in size to that used in
\cite{Bachant2016-BR-CFD} to approximatel (including blockage) the tow tank
experiments (3.66 m wide, 2.44 m tall, 1.52 m upstream and 2.16 m downstream),
with similar velocity boundary conditions: 1 m/s inflow, no-slip (fixed to 1
m/s) walls and bottom, and a rigid slip condition for the top, to approximate
some effects of the tow tank's free surface. Simulations were run for a total of
6 seconds, with the latter half used to calculate performance and wake
statistics. Pressure--velocity coupling for the momentum equation was achieved
using the PISO (pressure implicit splitting of operators) method. A slice of the
mesh in the $x$--$y$ plane is shown in Figure~\ref{fig:ALM-mesh}.

@@

The near-wake's mean velocity field at $x/D=1$ is shown in
Figure~\ref{fig:RVAT-ALM-LES-meancontquiv}. Compared with the RANS ALM results,
the LES looks much more like the blade-resolved and experimental results
\cite{Bachant2015-JoT}, showing the clockwise and counterclockwise mean swirling
motion on the $-y$ and $+y$ sides of the rotor, respectively.
